---
title: "TLEF Network Visualizations"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: "sandstone"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
library(tidyverse)
library(tidygraph)
library(visNetwork)
library(stringr)
source("networks.R")
```

```{r, include=FALSE}
all_tidy <- read_csv("../results/all_tidy.csv")
```

## All years

### All projects

* Only showing collaborators who are linked to 6 projects or more

```{r, echo = FALSE}
prepare_network_viz(
  raw_df = all_tidy,
  threshold = 6
)
```

### Large projects

* Only showing collaborators who are linked to 3 projects or more

```{r, echo = FALSE}
prepare_network_viz(
  raw_df = all_tidy,
  project_size_of_interest = "large",
  threshold = 3
)
```

### Small projects

* Only showing collaborators who are linked to 4 projects or more

```{r, echo = FALSE}
prepare_network_viz(
  raw_df = all_tidy,
  project_size_of_interest = "small",
  threshold = 4
)
```

## 2018

### All projects

* Only showing collaborators who are linked to 2 projects or more

```{r, echo = FALSE}
prepare_network_viz(
  raw_df = all_tidy,
  project_year_of_interest = 2018
)
```

### Large projects

* Only showing collaborators who are linked to 2 projects or more

```{r, echo = FALSE}
prepare_network_viz(
  raw_df = all_tidy,
  project_year_of_interest = 2018,
  project_size_of_interest = "large"
)
```

### Small projects

* Only showing collaborators who are linked to 2 projects or more

```{r, echo = FALSE}
prepare_network_viz(
  raw_df = all_tidy,
  project_year_of_interest = 2018,
  project_size_of_interest = "small"
)
```

## 2017

### All projects

* Only showing collaborators who are linked to 2 projects or more

```{r, echo = FALSE}
prepare_network_viz(
  raw_df = all_tidy,
  project_year_of_interest = 2017
)
```

### Large projects

* Only showing collaborators who are linked to 2 projects or more

```{r, echo = FALSE}
prepare_network_viz(
  raw_df = all_tidy,
  project_year_of_interest = 2017,
  project_size_of_interest = "large"
)
```

### Small projects

* Only showing collaborators who are linked to 2 projects or more

```{r, echo = FALSE}
prepare_network_viz(
  raw_df = all_tidy,
  project_year_of_interest = 2017,
  project_size_of_interest = "small"
)
```

## 2016

### All projects

* Only showing collaborators who are linked to 2 projects or more

```{r, echo = FALSE}
prepare_network_viz(
  raw_df = all_tidy,
  project_year_of_interest = 2016
)
```

### Large projects

* Only showing collaborators who are linked to 2 projects or more

```{r, echo = FALSE}
prepare_network_viz(
  raw_df = all_tidy,
  project_year_of_interest = 2016,
  project_size_of_interest = "large"
)
```

### Small projects

* Only showing collaborators who are linked to 2 projects or more

```{r, echo = FALSE}
prepare_network_viz(
  raw_df = all_tidy,
  project_year_of_interest = 2016,
  project_size_of_interest = "small"
)
```

## 2015

### All projects

* Only showing collaborators who are linked to 2 projects or more

```{r, echo = FALSE}
prepare_network_viz(
  raw_df = all_tidy,
  project_year_of_interest = 2015
)
```

### Large projects

* Only showing collaborators who are linked to 2 projects or more

```{r, echo = FALSE}
prepare_network_viz(
  raw_df = all_tidy,
  project_year_of_interest = 2015,
  project_size_of_interest = "large"
)
```

### Small projects

* Only showing collaborators who are linked to 2 projects or more

```{r, echo = FALSE}
prepare_network_viz(
  raw_df = all_tidy,
  project_year_of_interest = 2015,
  project_size_of_interest = "small"
)
```

## 2014

### All projects

* Only showing collaborators who are linked to 2 projects or more

```{r, echo = FALSE}
prepare_network_viz(
  raw_df = all_tidy,
  project_year_of_interest = 2014
)
```